*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-15 Code/Manuscript_O2.Rmd
initial edits to intro and captions

---
title: "*Prochlorococcus marinus* responses to light and oxygen" 
author:
  - name: '**Mireille Savoie**'
    affil: 1
    main: true
    email: msavoie@mta.ca
  - name: Aurora Mattison
    affil: 1,2
  - name: Julie Nadeau
    affil: 1
  - name: Laurel Genge
    affil: 1
  - name: Sylwia Śliwińska-Wilczewska
    affil: 1
  - name: Maximilian Berthold
    affil: 1,3
  - name: Naaman Omar
    affil: 1
  - name: Ondřej Prášil
    affil: 1,4
    main: false
  - name: Amanda M. Cockshutt
    affil: 1,5
    main: false
  - name: Douglas A. Campbell
    affil: 1
    main: false
    orcid: '0000-0001-8996-5463'
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Department of Biology, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 53 York St., Sackville NB, Canada, E4L 1C9.'
  - num: 2
institute:
  - ubc: 'Department of Biology, University of British Columbia'
  - num: 3
institute:
  - alga: 'MAX INSTITUTE'
  - num: 4
institute:
  - alga: 'Algatech, Czech Academy of Science'
  - num: 5
institute:
  - sfx: 'Department of Chemistry, St. Frances Xavier University'
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Manuscript_O2.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

Marine phytoplankton are ubiquitous and serve as an important base of the aquatic food chain. They contribute to more than 50% of the net global primary food production [@falkowskiOceanSciencePower2012], while comprising only a small fraction of the global primary producer biomass [@fieldPrimaryProductionBiosphere1998]. *Prochlorococcus marinus*, a genus of the phylum Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992]. Despite a small cell size, *P. marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of  global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].

@@

To the best of our knowledge, no other laboratory study has extensively examined the growth response of *Prochlorococcus* under such a diverse set of conditions. This study specifically focuses on evaluating how *Prochlorococcus* responds to varying [O~2~], different spectral wavebands, light levels and photoperiods. This comprehensive approach distinguishes this study from previous ones conducted on *Prochlorococcus* growth.

@@

ProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

@@

ProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein turnover complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",
                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

@@

```{r MED4ProteinAnotated, fig.cap = MED4ProteinAnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MED4ProteinAnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",

@@

knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnotated.png"))
```

@@

```{r MIT9313ProteinAnotated, fig.cap = MIT9313ProteinAnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313ProteinAnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",

@@

knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnotated.png"))
```

@@

# Acknowledgements
Jonah Sheinin assisted with growth of some cultures for protein analyses.

>>>>

---
title: "*Prochlorococcus marinus* responses to light and oxygen" 
author:
  - name: '**Mireille Savoie**'
    affil: 1
    main: true
    email: msavoie@mta.ca
  - name: Aurora Mattison
    affil: 1,2
  - name: Julie Nadeau
    affil: 1
  - name: Laurel Genge
    affil: 1
  - name: Sylwia Śliwińska-Wilczewska
    affil: 1
  - name: Maximilian Berthold
    affil: 1,3
  - name: Naaman Omar
    affil: 1
  - name: Ondřej Prášil
    affil: 1,4
    main: false
  - name: Amanda M. Cockshutt
    affil: 1,5
    main: false
  - name: Douglas A. Campbell
    affil: 1
    main: false
    orcid: '0000-0001-8996-5463'
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Department of Biology, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 53 York St., Sackville NB, Canada, E4L 1C9.'
  - num: 2
institute:
  - ubc: 'Department of Biology, University of British Columbia'
  - num: 3
institute:
  - umwelt: 'Umweltbundesamtm, Dessau-Roßlau, Germany'
  - num: 4
institute:
  - alga: 'Algatech, Czech Academy of Science'
  - num: 5
institute:
  - sfx: 'Department of Chemistry, St. Frances Xavier University'
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Manuscript_O2.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

*Prochlorococcus marinus*, a genus of the phylum Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992]. Despite a small cell size, *P. marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of  global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].

@@

This study focuses on evaluating how growth of *Prochlorococcus* strains from different clades responds to varying [O~2~], spectral wavebands, light levels and photoperiods.

@@

ProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
                       "Point colours identify *Prochlorococcus* clade assignments",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

@@

ProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
                       "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",
                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
                       "Point colours identify *Prochlorococcus* clade assignments",
                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
 .sep = " ")

@@

```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MED4ProteinAnnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",

@@

knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnnotated.png"))
```

@@

```{r MIT9313ProteinAnmotated, fig.cap = MIT9313ProteinAnmotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313ProteinAmnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",

@@

knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnnotated.png"))
```

@@

# Acknowledgements
Jonah Sheinin assisted with growth of some cultures for protein analyses, while Carlie Barnhill assisted with code for import of multicultivator growth data files.
